\normalmarginpar\marginnote{\section*{Gameplay}
Your goal is to be the first player to deduce which letter or number is depicted in the original image.

To do so, you will need to use information from your player sheet and from your opponents'.

Take turns asking each other questions about your grids. Each question must be addressed to a single player and must identify a single icon location.

When you are asked a question, you must answer by announcing whether the specified icon on your sheet is an \scalebox{0.75}{\drawtwostar{}} or an \scalebox{0.75}{\drawonestar{}}.

After you ask a question, you may try to solve the puzzle. If you do, write your solution on your player sheet. Then turn your sheet face down. You will not participate in the remainder of the game.

When everyone has committed to a solution, compare any two grids to find the original image. The first player who committed to the correct solution wins.

%\begin{enumerate}[leftmargin=*]
%\item Partition the players into groups with two or three players in each group.
%\item Start the timer. Try to memorize the portraits that appear on your player sheet.
%\item When time expires, turn your player sheet over so that you cannot see the portraits displayed thereon.
%\item Describe the portraits that appear on your sheet to the other players in your group. Try to identify a portrait that appears on more than one of your player sheets.
%\item Finally, each player should simultaneously choose one of the portraits on the Mugshots Gallery. If everyone in your group chose a portrait that appears on more than one of your player sheets, you win! 
%\end{enumerate}
}[-16.5cm]
\reversemarginpar\marginnote{\raggedright\section*{Overview}
Cryptoglyph is a deduction game for two to six players which can be played in about ten minutes.

You will need a set of player sheets that all have the same random seed value. Each player will need a player sheet with a unique sequence number and something to write with.

\textbf{Note:} You should not show your player sheet to any other player.

A 5x5 grid of \emph{blocks} is displayed on each player sheet. There are six possible blocks. Each block has two \scalebox{0.75}{\drawtwostar{}} icons and two \scalebox{0.75}{\drawonestar{}} icons.

Each grid is one \emph{share} of a distributed encryption of an image which depicts either a letter or a single-digit number. 

%The grids on the player sheets depend on the original image.

If a block in the original image is white, then every player sheet will have the same randomly chosen block in that position.

Otherwise, each player sheet will have a different randomly chosen block in that position.

}[-16.5cm]
